\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://benjaminkrueger.xyz/}{\Large Benjamin Krueger}} & Email : \href{mailto:benjamin.oliver.krueger@gmail.com}{benjamin.oliver.krueger@gmail.com}\\
  \href{https://benjaminkrueger.xyz/}{Personal Site: benjaminkrueger.xyz} & Mobile : +1-573-612-8937 \\
  \href{https://github.com/benkrueger}{Github: https://github.com/benkrueger} & \href{https://www.linkedin.com/in/benjamin-krueger/}{Linkedin: https://www.linkedin.com/in/benjamin-krueger/} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University Of Missouri St Louis}{St Louis, Missouri}
      {Bachelor of Science in Computer Science;  GPA: 3.25 }{Aug. 2020 -- Aug. 2022}
    \resumeSubheading
      {Missouri University Of Science and Technology}{Rolla, MO}
      {Bachelors of Science in Computer Science (transferred)  }{Aug. 2015 -- Jul. 2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Accenture Federal Services}{St Louis}
      {Sr. Software Engineering analyst}{May 2022 - Present}   
      \resumeItemListStart
        \resumeItem{CMS FFM}{Worked on the healthcare.gov team as a DevOps engineer.}
        \resumeItem{Agile DevOps}{Worked on an agile DevOps team focused on supporting developer shared services and production infrastructure across multiple environments.}
        \resumeItem{CI/CD}{Wrote and managed Jenkins CI/CD build pipelines. Utilized Jenkins, Nexus3 and ansible to build, package and deploy various applications and services to production, testing and internal use.}
        \resumeItem{Security Automation}{Developed automated vulnerability and secret scanning pipelines for source code hosted on Github enterprise.}
        \resumeItem{Infrastructure as Code}{Configured, deployed, and updated live AWS infrastructure running shared services utilizing Jenkins and Ansible with a GitOps workflow.}
        \resumeItem{Analysis}{Wrote detailed technical documents analyzing software engineering toolchains and infrastructure. Analyzed system architecture and source code to improve security.}
        \resumeItem{Research and Presentation}{Researched various emerging technologies and gave a weekly touchpoint presentation to encourage innovation.}
        \resumeItem{Github Enterprise Administration}{Github Enterprise Administrator for our internal GHE instance. Managed access controls, teams, organizations and repos. Wrote Github Enterprise reporting and automation tooling in Python and Groovy.}
        \resumeItem{Cross Team Collaboration}{Coordinated various infrastructure improvements and upgrades to infrastructure across development, infrastructure and security teams.}
      \resumeItemListEnd
    \resumeSubheading
      {Omni Federal}{Remote}
      {Software Engineer}{August 2021 - Febuary 2022}   
      \resumeItemListStart
        \resumeItem{SABER}{ Collaborated on a team responsible for the development of a newly commissioned web application for use in air force strategic resource planning.}
        \resumeItem{SecDevOps}{Deployed applications to a secure government cloud platforms through a secure build pipeline utilizing gitops, gitlab and terraform.}
        \resumeItem{Security Auditing}{Documented application security architecture per secure platform requirements.}
        \resumeItem{Agile Web Development}{Developed features, fixed bugs, and maintained codebase in a React/Node/MySQL environment following the agile process.}
      \resumeItemListEnd
    \resumeSubheading
      {United States Geological Survey}{Rolla, MO}
      {Student Software Contractor}{Jan 2020 - Jan 2021}   
      \resumeItemListStart
        \resumeItem{Unit Testing}{Unit tested python and c++ GIS data processing software.}
        \resumeItem{Refactoring}{Refactored python and c++ GIS data processing software.}
        \resumeItem{GIS}{Automated GIS data processing with GDAL.}
        \resumeItem{Web Testing}{Wrote automated frontend tests in python utilizing Selenium.}
        \resumeItem{Web Development}{Utilized Django, Postgres, Javascript and HTML to implement GIS specification web application.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Hunter Engineering}{Bridgeton, MO}
      {Software Engineering Intern}{Jan 2019 - Aug 2019}
      \resumeItemListStart
        \resumeItem{Agile}{Collaborated with a team to following Agile development methodologies.}
        \resumeItem{Testing}{Followed a test driven development workflow for c\# microservice development.}
        \resumeItem{Cloud}{Utilized Azure DevOps workflow to automate builds, tests, and static code analysis.}
        \resumeItem{Development}{Implemented native libraries in c++ with c\# bindings.}
        \resumeItem{Microservices}{Helped team deliver microservice distributed system in c++ and c\#.}
      \resumeItemListEnd

    \resumeSubheading
      {Missouri University Of Science and Technology}{Rolla, MO}
      {IT Student Co-op}{Jun 2017 - Jan 2018}
      \resumeItemListStart
        \resumeItem{Management}
          {Lead a team of part time student employees delegating desktop administration tasks.}
        \resumeItem{Active Directory}
          {Wrote active directory group policy for desktop administration.}
        \resumeItem{Desktop Administration}{Performed all roles related to packaging, updating and licensing desktop software.}
      \resumeItemListEnd
    \resumeSubSubheading{IT Student Employee}{Jun 2016 - Nov 2019 }
        \resumeItemListStart
        \resumeItem{Softare Packaging}{Developed and tested desktop software packages with Perl and System Center Configuration Manager.}
        \resumeItem{Desktop Administration}{Provisioned and deployed desktops, virtual machines and sotware packaged with SCCM.}
        \resumeItem{VDI Software}{Packaged desktop software for VDI streaming.}
        \resumeItem{Troubleshooting}{Resolved various deployment and configuration issues in desktop lab environment.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%Undergrad Cert

\section{Certifications}
\resumeSubHeadingListStart
    \item{\textbf{Security+}}{: CompTIA}
\resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, C++, SQL, Java, Perl,Javascript, C\#, Bash, Groovy}
      \hfill
    }
    \item{
        \textbf{Technologies}{: VMware, GDAL,  Django, Postgres, Bootstrap, Linux, Docker, Jenkins, AWS, Trufflehog, Github Enterprise, ZAproxy, Ansible, Selenium, Gradle, Maven, SonarQube, Nexus}
        \hfill
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}